Quantum Pseudo-Telepathy

### 2023-06-05 paper/main.tex
example env

@@

\subsection{Classical Solution}
\label{sec:classic-sol}

Assume that Alice and Bob decided to adopt a deterministic strategy.
For that, they met before the beginning of the game, and prepared
their answers for each possible row and column. For example, they
might have agreed that, if given the first column, Bob shall fill it
with three \(-1\)'s. Then, whatever row Alice is given, she must fill
it with either \(\{-1, +1, -1\}\) or \(\{-1, -1, +1\}\). Suppose that
Alice decided that she would fill any row in the same way:
\(\{-1, -1, +1\}\). Figure~\ref{fig:classical} (a) shows how the
predefined matrix would look like. Notice that Alice's rows are
already defined, but Bob still has to decide how to fill the second
and third columns. He can, and must, fill the second column with three
\(-1\)'s, so that whatever row Alice is given, the intersection
agrees. Intuitively, for the same reason, he should then fill the
third column with three \(+1\)'s. However, this is not a valid
strategy, since the product of the last column will be \(+1\) and not
\(-1\), as required. Thus, Bob must fill at least one of the
entries of the last column with \(-1\).  By doing that, there will be
one row and column whose intersection does not agree, and thus one row
and column for which Alice and Bob lose, as illustrated in
Figure~\ref{fig:classical} (b). It is not difficult to convince yourself that,
no matter how Alice and Bob decide to fill in their entries, it is impossible
for them to come up with predefined answers that always win. In fact,
the best that they can do is to win with probability \(\nicefrac{8}{9}\).

{\renewcommand{\arraystretch}{2}
\begin{figure}
  \centering
  \begin{subfigure}[t]{0.475\textwidth}
    \[\begin{array}{|>{\quad\columncolor{gray!50}}c<{\quad}|*{2}{>{\quad}c<{\quad}|}}
        \hhline{---}
        -1 & -1 & +1 
        \\ \hhline{---}
        -1 & -1 & +1 
        \\ \hhline{---}
        -1 & -1 & +1 
        \\ \hhline{---}
      \end{array}\]
    \caption{Initially, Alice and Bob agree that Bob shall fill the
      first column with \(\{-1, -1, -1\}\). Based on this choice,
      Alice decides to fill all of her rows with
      \(\{-1, -1, +1\}\).}
  \end{subfigure}
  \hfill{}
  \begin{subfigure}[t]{0.475\textwidth}
    \[\begin{array}{|*{3}{>{\quad\columncolor{gray!50}}c<{\quad}|}}
        \hhline{---}
        -1 & -1 & \cellcolor{red!80!black!55}\pm 1
        \\ \hhline{---}
        -1 & -1 & +1
        \\ \hhline{---}
        -1 & -1 & +1
        \\ \hhline{---}
      \end{array}\]
    \caption{Bob has to fill the second column with \(-1\)'s, to match
      Alice's choice. He should also match Alice's choice for each
      cell of the third column, but he cannot, for the product of
      the column must be \(-1\).}
  \end{subfigure}
  \caption{One possible classical deterministic strategy for the Magic
    Square game. Following this predefined strategy, Alice and Bob
    lose when assigned, respectively, the first row and third column,
    but win in any other scenario. That is, their probability of
    winning a round is \(\nicefrac{8}{9}\). Gray cells are entries for
    which Alice's and Bob's choices agree.\label{fig:classical}}
\end{figure}}

>>>>

\usepackage{float}
\usepackage{tcolorbox}
\tcbuselibrary{theorems}

\newtcbtheorem{tcbexample}{Example}{
  colback=gray!15,
  colbacktitle=gray!15,
  coltitle=red!75!black,
  fonttitle=\bfseries,
  detach title,
  before upper={\tcbtitle},
  separator sign none,
  description delimiters={(}{). }
}{ex}

@@

\subsection{Classical Solution}
\label{sec:classic-sol}
Assume that Alice and Bob decided to adopt a deterministic strategy.
For that, they met before the beginning of the game, and prepared
their answers for each possible row and column. In this scenario,
what is the best strategy that they can come up with?

\begin{tcbexample}{Classical, Deterministic Solution}{classic-sol}
  Alice and Bob might have agreed that, if given the first column, Bob shall fill it
  with three \(-1\)'s. Then, whatever row Alice is given, she must fill
  it with either \(\{-1, +1, -1\}\) or \(\{-1, -1, +1\}\). Suppose that
  Alice decided that she would fill any row in the same way:
  \(\{-1, -1, +1\}\). Figure~\ref{fig:classical} (a) shows how the
  predefined matrix would look like. Notice that Alice's rows are
  already defined, but Bob still has to decide how to fill the second
  and third columns. He can, and must, fill the second column with three
  \(-1\)'s, so that whatever row Alice is given, the intersection
  agrees. Intuitively, for the same reason, he should then fill the
  third column with three \(+1\)'s. However, this is not a valid
  strategy, since the product of the last column will be \(+1\) and not
  \(-1\), as required. Thus, Bob must fill at least one of the
  entries of the last column with \(-1\).  By doing that, there will be
  one row and column whose intersection does not agree, and thus one row
  and column for which Alice and Bob lose, as illustrated in
  Figure~\ref{fig:classical} (b).

  {\renewcommand{\arraystretch}{2}
    \begin{figure}[H]
      \centering
      \begin{subfigure}[t]{0.475\textwidth}
        \[\begin{array}{|>{\quad\columncolor{gray!50}}c<{\quad}|*{2}{>{\quad}c<{\quad}|}}
            \hhline{---}[
            -1 & -1 & +1 
            \\ \hhline{---}
            -1 & -1 & +1 
            \\ \hhline{---}
            -1 & -1 & +1 
            \\ \hhline{---}
          \end{array}\]
        \caption{Initially, Alice and Bob agree that Bob shall fill the
          first column with \(\{-1, -1, -1\}\). Based on this choice,
          Alice decides to fill all of her rows with
          \(\{-1, -1, +1\}\).}
      \end{subfigure}
      \hfill{}
      \begin{subfigure}[t]{0.475\textwidth}
        \[\begin{array}{|*{3}{>{\quad\columncolor{gray!50}}c<{\quad}|}}
            \hhline{---}
            -1 & -1 & \cellcolor{red!80!black!55}\pm 1
            \\ \hhline{---}
            -1 & -1 & +1
            \\ \hhline{---}
            -1 & -1 & +1
            \\ \hhline{---}
          \end{array}\]
        \caption{Bob has to fill the second column with \(-1\)'s, to match
          Alice's choice. He should also match Alice's choice for each
          cell of the third column, but he cannot, for the product of
          the column must be \(-1\).}
      \end{subfigure}
      \caption{One possible classical deterministic strategy for the Magic
        Square game. Following this predefined strategy, Alice and Bob
        lose when assigned, respectively, the first row and third column,
        but win in any other scenario. That is, their probability of
        winning a round is \(\nicefrac{8}{9}\). Gray cells are entries for
        which Alice's and Bob's choices agree.\label{fig:classical}}
    \end{figure}}
\end{tcbexample}

Example~\ref{ex:classic-sol} illustrates one of the many deterministic
strategies that Alice and Bob can adopt. It is not difficult to
convince yourself that, no matter how they decide to fill in
their entries, it is impossible for them to come up with predefined
answers that always win. Any deterministic strategy is a pair of
matrices, one for Alice and another for Bob. The only way that they could
design a strategy that wins with certainty every round is to prepare two
identical matrices satisfying the requirements for each row and for each
column. That is, a single matrix for which the product of every row is
\(+1\) and the product of every column is \(-1\). Such a matrix cannot
possibly exist! It turns out that the best that they can do is to win
with probability \(\nicefrac{8}{9}\).
